---
title: "TFM_2"
author: "Enrique Perez"
date: "2023-04-26"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(fda)
library(roahd)
library(tidyr)
library(ggplot2)
library(reshape2)
library(graphics)
```

```{r}
scale_data <- function(data, scale_method = "0,1") {
  if (scale_method == "0,1") {
    #### Scale the data in the [0,1] interval and separate train and test ####
    
    maxs <- apply(data, 2, max) # obtain the max of each variable
    mins <- apply(data, 2, min) # obtain the min of each variable
    output <- as.data.frame(scale(data, center = mins, scale = maxs - mins))
  } else if (scale_method == "-1,1") {
    #### Scale the data in the [-1,1] interval ####
    
    maxs <- apply(data, 2, max) # obtain the max of each variable
    mins <- apply(data, 2, min) # obtain the min of each variable
    output <- as.data.frame(scale(data, center = mins + (maxs - mins) / 2, scale = (maxs - mins) / 2))
  } else if (scale_method == "standardize") {
    #### Scale the data to have mean=0 and sd=1 and separate train and test ####
    
    output <- as.data.frame(scale(data, center = TRUE, scale = TRUE))
  } else {
    print("Non valid method")
    output <- "Non valid method"
  }
  
  return(output)
}
```


```{r}
#Call to the codes to obtain the indexes and to create the functional multivariate boxplot
source("C:/Users/enriq/Desktop/UNIVERSIDAD/Máster en Big Data/TFM/Code/indexes.R")
source("C:/Users/enriq/Desktop/UNIVERSIDAD/Máster en Big Data/TFM/Code/fmboxplot.R")
#Call to the code that simulates the data
source("C:/Users/enriq/Desktop/UNIVERSIDAD/Máster en Big Data/TFM/Code/datos_multivariantes_simulados/simulation_model_workshop_Belen/simulator_eigen2.R")

```


# ######################################## #
#  PARTE DEL CÓDIGO DE BELÉN QUE ME SIRVE  #
# ######################################## #

### ECG data

```{r}
temp = CanadianWeather$dailyAv[,,"Temperature.C"]
prec = CanadianWeather$dailyAv[,,"Precipitation.mm"]
# Scale data
temp_sc <- scale_data(temp,scale_method = "standardize")
prec_sc <- scale_data(prec,scale_method = "standardize")

t <- seq(1,365,length=dim(temp)[1])

datos <- array(dim=c(35,365,2))
 datos[,,1] <- t(temp_sc)
 datos[,,2] <- t(prec_sc)
#datos[,,1] <- t(temp)
#datos[,,2] <- t(prec)
```


# MAIN FUNCTION

```{r, warning=FALSE}
rangeval <- c(min(t),max(t))
nbasis <- 30
norder <- 4
#Run the fmboxplot function on our data
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
gridExtra::grid.arrange(p1,p2, nrow = 1)
```

```{r}
res<-fmboxplot_i(prec_sc, t, rangeval, nbasis, norder)
(plot<-res$plot)
```

```{r}
res<-fmboxplot_i(temp_sc, t, rangeval, nbasis, norder)
(plot<-res$plot)
```


# SIMULATIONS

## Model 0

### First variant

```{r}
set.seed(122)
t <- seq(0,1, length.out = 50)
rangeval <- c(min(t),max(t))
nbasis <- 30
norder <- 4

ssm0_0 <- multimodel0_0()

dt1 <- ssm0_0[[1]]@X; dt2 <- ssm0_0[[2]]@X; dt3 <- ssm0_0[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)

```

### Second variant

```{r}
ssm0_1 <- multimodel0_1()

dt1 <- ssm0_1[[1]]@X; dt2 <- ssm0_1[[2]]@X; dt3 <- ssm0_1[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 1

### First variant

```{r}
set.seed(145)
ssm <- multimodel1(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X;

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```
```{r}
real_outliers<-c(1:10)
correct<-0
for (i in outliers) {
  if(i %in% real_outliers){correct<-correct+1}
}
(TPR<-correct/length(real_outliers)) # Porcentaje de acierto
(FPR<-(length(outliers)-correct)/length(outliers)) #Porcentaje false positives
correct<-0
for (i in out1) {
  if(i %in% real_outliers){correct<-correct+1}
}
(TPR1<-correct/length(real_outliers)) 
(FPR1<-(length(out1)-correct)/length(out1)) 
correct<-0
for (i in out2) {
  if(i %in% real_outliers){correct<-correct+1}
}
(TPR<-correct/length(real_outliers))
(FPR<-(length(out2)-correct)/length(out2)) 
correct<-0
for (i in out3) {
  if(i %in% real_outliers){correct<-correct+1}
}
(TPR<-correct/length(real_outliers))
(FPR<-(length(out3)-correct)/length(out3))
```

### Second variant

```{r}
ssm <- multimodel1(n_outliers = 10, specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel1(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X;  

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 2

### First variant

```{r}
ssm <- multimodel2(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel2(n_outliers = 10, specialp = c(1,2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X;  

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel2(n_outliers = 10, specialp = c(1))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 3

### First variant

```{r}
ssm <- multimodel3(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X;  

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel3(n_outliers = 10,
                   specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel3(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 4

### First variant

```{r}
ssm <- multimodel4(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel4(n_outliers = 10,
                   specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel4(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 5

### First variant

```{r}
ssm <- multimodel5(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel5(n_outliers = 10,
                   specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel5(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X;

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fourth Variant

```{r}
ssm <- multimodel5(n_outliers = 10, specialp = c(2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fifth Variant

```{r}
ssm <- multimodel5(n_outliers = 10, specialp = c(1,2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 6

### First variant

```{r}
ssm <- multimodel6(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel6(n_outliers = 10,
                   specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel6(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fourth variant

```{r}
ssm <- multimodel6(n_outliers = 10, specialp = c(2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fifth variant

```{r}
ssm <- multimodel6(n_outliers = 10, specialp = c(1,2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 7

### First variant

```{r}
ssm <- multimodel7(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel7(n_outliers = 10,
                   specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel7(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fourth variant

```{r}
ssm <- multimodel7(n_outliers = 10, specialp = c(2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fifth variant

```{r}
ssm <- multimodel7(n_outliers = 10, specialp = c(1,2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 8

### First variant

```{r}
ssm <- multimodel8(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel8(n_outliers = 10,
                   specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel8(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fourth variant

```{r}
ssm <- multimodel8(n_outliers = 10, specialp = c(2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fifth variant

```{r}
ssm <- multimodel8(n_outliers = 10, specialp = c(1,2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

## Model 9

### First variant

```{r}
ssm <- multimodel9(n_outliers = 10)

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Second variant

```{r}
ssm <- multimodel9(n_outliers = 10,
                   specialp = c(1,3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Third variant

```{r}
ssm <- multimodel9(n_outliers = 10, specialp = c(3))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fourth variant

```{r}
ssm <- multimodel9(n_outliers = 10, specialp = c(2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```

### Fifth variant

```{r}
ssm <- multimodel9(n_outliers = 10, specialp = c(1,2))

dt1 <- ssm[[1]]@X; dt2 <- ssm[[2]]@X; dt3 <- ssm[[3]]@X; 

datos <- array(dim=c(100,50,3))
datos[,,1]<-dt1
datos[,,2]<-dt2
datos[,,3]<-dt3
pa<-param(datos, t, rangeval, nbasis, norder)
p1<-fmboxplot(1,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p2<-fmboxplot(2,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
p3<-fmboxplot(3,pa$results,pa$pq1,pa$pq3,pa$pw1,pa$pw3,pa$outliers)
outliers<-pa$outliers
r1<-fmboxplot_i(t(dt1), t, rangeval, nbasis, norder)
p1_i<-r1$plot ; out1<-r1$outliers
r2<-fmboxplot_i(t(dt2), t, rangeval, nbasis, norder)
p2_i<-r2$plot ; out2<-r2$outliers
r3<-fmboxplot_i(t(dt3), t, rangeval, nbasis, norder)
p3_i<-r3$plot ; out3<-r3$outliers

gridExtra::grid.arrange(p1,p2,p3,p1_i, p2_i, p3_i, nrow = 2)
```


